Taking Dyads Seriously\thanks{Based upon joint works with Michael Ward (Duke University), Cassy L. Dorff (University of New Mexico), Max Gallop (University of Strathclyde), Juan Tellez (Duke University), Howard Liu (Duke University), \& Margaret Foster (Duke University). }

### 2018-02-11 prezzy/netsMatterDeck.tex
prezzy

\title[AMEN]{Taking Dyads Seriously\thanks{Based upon joint works with Michael Ward (Duke University), Cassy L. Dorff (University of New Mexico), Max Gallop (University of Strathclyde), Juan Tellez (Duke University), Howard Liu (Duke University), \& Margaret Foster (Duke University). This is also part of a broader project involving Peter Hoff (Duke University) and Michael Ward.}
}

\author{Shahryar Minhas\\Cassy L. Dorff\\Margaret Foster\\Max Blau Gallop\\Juan Tellez\\ Michael D. Ward}
%{Shahryar Minhas\\ minhassh@msu.edu \\ s7minhas.com \\
%Michigan State University}

\date{\today}

@@

Thank you!

@@

\frame{
  \frametitle{Actual Code}
\# running in parallel varying k\\
imps = 10000 ; brn = 25000 ; ods = 10 ; latDims = 0:3\\
\# Run amen in parallel
library(doParallel) ; library(foreach) ; cl=makeCluster(4) \\ registerDoParallel(cl)\\
foreach(ii=1:length(latDims), .packages=c("amen")) \%dopar\% {\\
  \# load previous model run\\
  load(prevModelFiles[ii])\\
  \# extract start vals\\
  startVals0 = ameFit\$'startVals'\\
  \# dump rest\\ 
  rm(ameFit)\\
   ameFit = ame\_repL(\\
    Y=yList,Xdyad=xDyadList,Xrow=NULL,Xcol=NULL, \\
    model="bin",symmetric=FALSE,intercept=TRUE,R=latDims[ii], \\
    nscan=imps, seed=1, burn=brn, odens=ods, \\
    plot=FALSE, print=FALSE, gof=TRUE, startVals=startVals0,\\
    periodicSave=TRUE ) \\    
  save(ameFit, file=paste0('model\_k', latDims[ii],'\_v2.rda') )\\
}
stopCluster(cl)
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Backup Slides}
\frame{\frametitle{backup slides}
Go ahead, ask me about ERGM. }

>>>>

\title[AMEN]{Taking Dyads Seriously\thanks{Based upon joint works with Michael Ward (Duke University), Cassy L. Dorff (University of New Mexico), Max Gallop (University of Strathclyde), Juan Tellez (Duke University), Howard Liu (Duke University), \& Margaret Foster (Duke University). 
}}

\author{Michael D. Ward}
%{Shahryar Minhas\\ minhassh@msu.edu \\ s7minhas.com \\
%Michigan State University}

\date{\today\\ 2018 Asian Political Methodology Meeting\\Asia Center\\Seoul National University\\Seoul, Korea}

@@

Thank you!  Thanks especially to Jong Hee Park and the Organizing Committee.

@@

\frame{
  \frametitle{Actual Code}
  {\footnotesize
\# running in parallel varying k\\
imps = 10000 ; brn = 25000 ; ods = 10 ; latDims = 0:3\\
library(doParallel) ; library(foreach) ; cl=makeCluster(4) \\ registerDoParallel(cl)\\
foreach(ii=1:length(latDims), .packages=c("amen")) \%dopar\% {\\
  \# load previous model run\\
  load(prevModelFiles[ii])\\
  \# extract start vals\\
  startVals0 = ameFit\$'startVals'\\
  \# dump rest\\ 
  rm(ameFit)\\
   ameFit = ame\_repL(\\
    Y=yList,Xdyad=xDyadList,Xrow=NULL,Xcol=NULL, \\
    model="bin",symmetric=FALSE,intercept=TRUE,R=latDims[ii], \\
    nscan=imps, seed=1, burn=brn, odens=ods, \\
    plot=FALSE, print=FALSE, gof=TRUE, startVals=startVals0,\\
    periodicSave=TRUE ) \\    
  save(ameFit, file=paste0('model\_k', latDims[ii],'\_v2.rda') )\\
}
stopCluster(cl)
}
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Backup Slides}
\frame{\frametitle{backup slides}
Go ahead, ask me about ERGM. }
